\problemname{Spies Like Us}

The Ultrasecret Spy Organization is very concerned about recent leads
concerning a secret conspiracy involving the use of the Comic Sans font.

In order to avoid groupthink, the Ultrasecret Spy Organization has decided to
divide its agents in two groups. Each of the two groups will carry its own
investigation. However, occasionally interaction between members of different
groups will happen through some previously designated contact points (i.e., two
people on different teams that are allowed to speak with each other in special
circumstances). This has to be made in a way that preserves the fact that there
is not much communication between the teams. To make this rule more exact, two
people on the same team can have no more than one common contact on the other
team.

You are given a plan for the contact points between the two groups. Your task
is to determine whether this actually satisfies the constraint that two people
on the same team can have no more than one common contact in the other team.

\section*{Input}

The first line of the input file will contain two space-separated integers $N$
and $M$ ($1 \leq N, M \leq 5\,000$). They represent the number of people in each of the
teams. The next line will contain an integer $K$ ($0 \leq K \leq NM$). Each of the
following $K$ lines will contain two integers, $i$ and $j$, with ($1 \leq i \leq N$, $1 \leq j \leq M$).
This input will represent that person $i$ of the first team and person $j$ of the
second team are allowed to communicate with each other.

\section*{Output}

For each input, you will output one line. Its content will be YES, if the
proposal satifies the constraint that two people on the same team can have no
more than one common contact on the other team, and NO otherwise.
